---
title: "R Notebook"
output: html_notebook
---
***
###Creating PPP

Import the traffic dataset and coverting the crs from WGS84 to SVY21, at the same time, fixing the x and y for ppp function later. Result is exported to a temp csv file located in /data.
```{r}
library(readr)
library(sf)
trafficReport <- read_csv("data/LTATrafficDataClean2.csv")
trafficReport_shp <- st_as_sf(trafficReport, coords = c("Longitude", "Latitude"), crs = "+proj=longlat +datum=WGS84 +no_defs")
traffic_Report_svy21 <- st_transform(trafficReport_shp, crs = 3414)
st_write(traffic_Report_svy21, "data/temp.csv", layer_options = "GEOMETRY=AS_XY") # writes X and Y as columns
```

***
Import in SG map to act as owin
```{r}
library(rgdal)
library(polyCub) #install package polyCub
costaloutline <- readOGR("data/sg_map/CostalOutline.shp")
costaloutline_sp <- as(costaloutline, "SpatialPolygons")
costaloutline_owin <- as.owin.SpatialPolygons(costaloutline_sp)
costaloutline_mask <- as.mask(costaloutline_owin)
```


***
Reading the temp csv and creating the ppp
```{r}
library(tidyverse)
library(spatstat)
temp <- read_csv("data/temp.csv")
accidents <- temp %>% filter(Type == "Accident")
roadworks <- temp %>% filter(Type == "Roadwork")
heavytraffic <- temp %>% filter(Type == "Heavy Traffic")
accidents_ppp <- ppp(accidents$X, accidents$Y, costaloutline_owin)
roadworks_ppp <- ppp(roadworks$X, roadworks$Y, costaloutline_owin)
heavytraffic_ppp <- ppp(heavytraffic$X, heavytraffic$Y, costaloutline_owin)
plot(accidents_ppp)
plot(roadworks_ppp)
plot(heavytraffic_ppp)
```

##Preparing the linnet
```{r}
library(maptools)
roadNetwork <- readShapeSpatial("data/RoadNetwork/roads_expressway", CRS("+init=epsg:3414"))
roadNetwork_psp <- as.psp(roadNetwork, window=NULL, marks=NULL, check=spatstat.options("checksegments"), fatal=TRUE)
roadNetwork_linnet <- as.linnet.psp(roadNetwork_psp, sparse=TRUE)
plot(roadNetwork_linnet)
```

##LPP
Generating the LPP

```{r}
accidents_lpp <- lpp(accidents_ppp, roadNetwork_linnet)
heavytraffic_lpp <- lpp(heavytraffic_ppp, roadNetwork_linnet)
plot(accidents_lpp)
plot(heavytraffic_lpp)
```

***
###K Function
Plotting the K function
```{r}
plot(linearK(accidents_lpp, correction="none", ratio=FALSE))
```

***
###Kernel Density Estimation
Plotting the KDE
```{r}
library(spatstat)
plot(density.lpp(accidents_lpp, 1000))
plot(density.ppp(accidents_ppp, sigma=bw.ppl))
plot(density.lpp(heavytraffic_lpp, 3000))
plot(density.ppp(heavytraffic_ppp, 1000))
```


***
###K Nearest Neighbour
Plotting the knn
```{r}
library(spatstat)
hist(nndist.lpp(accidents_lpp, k=10, method="C"))
plot(nnfun.lpp(accidents_lpp, k=10, method="C"))
plot(envelope(accidents_ppp, Gest, nsim = 99, rank = 1, glocal = TRUE), xlim=c(0,10000))
hist(nndist.lpp(heavytraffic_lpp, k=10, method="C"))
plot(nnfun.lpp(heavytraffic_lpp, k=10, method="C"))
plot(envelope(heavytraffic_ppp, Gest, nsim = 99, rank = 1, glocal = TRUE), xlim=c(0,6000))
```

***
###Interactive map on accidents
Storing the accident KDE to variable

```{r}
library(spatstat)
accidentskde <- density.lpp(accidents_lpp, sigma=1)
plot(accidentskde)
```
Convert accident kde to spatialgriddataframe and using tmap to plot

```{r}
library(tmap)
library(tmaptools)
library(maptools)

accidentkde_sgdf <- as.SpatialGridDataFrame.im(accidentskde)
spplot(accidentkde_sgdf)

proj4string(accidentkde_sgdf) = CRS("+init=epsg:3414")

tmap_mode("view")
qtm(accidentkde_sgdf)
```

***
###Interactive map for heavy traffic
Storing the heavy traffic KDE to variable

```{r}
library(spatstat)
heavytraffickde <- density.lpp(heavytraffic_lpp, sigma=1)
plot(heavytraffickde)
```

Convert heavy traffic kde to spatialgriddataframe and using tmap to plot

```{r}
library(tmap)
library(tmaptools)
library(maptools)

heavytraffickde_sgdf <- as.SpatialGridDataFrame.im(heavytraffickde)
spplot(heavytraffickde_sgdf)

proj4string(heavytraffickde_sgdf) = CRS("+init=epsg:3414")

tmap_mode("view")
qtm(heavytraffickde_sgdf)
```
