---
title: "R Notebook"
output: html_notebook
---
***
### Loading R Packages

```{r}
packages = c('tmap', 'sf', 'tidyverse', 'RColorBrewer', 'classInt', 'spatstat', 'rgdal', 'maptools')
for (p in packages){
  if(!require(p, character.only = T)){
  install.packages(p)
}
library(p, character.only = T)
}
```

***
###Creating PPP

Import the traffic dataset and coverting the crs from WGS84 to SVY21, at the same time, fixing the x and y for ppp function later. Result is exported to a temp csv file located in /data.
```{r}
library(readr)
library(sf)
# trafficReport <- read_csv("data/LTATrafficDataClean2.csv")
# trafficReport_shp <- st_as_sf(trafficReport, coords = c("Longitude", "Latitude"), crs = "+proj=longlat +datum=WGS84 +no_defs")
# traffic_Report_svy21 <- st_transform(trafficReport_shp, crs = 3414)
```

***
Import in SG map to act as owin
```{r}
library(rgdal)
library(polyCub) #install package polyCub
costaloutline <- readOGR("data/sg_map/CostalOutline.shp")
costaloutline_sp <- as(costaloutline, "SpatialPolygons")
costaloutline_owin <- as.owin.SpatialPolygons(costaloutline_sp)
costaloutline_mask <- as.mask(costaloutline_owin)
```


***
Reading the temp csv and creating the ppp
```{r}
library(tidyverse)
library(spatstat)
accidents <- readOGR(dsn = "final_data",  layer = "accidents")
accidents_sp <- as(accidents, 'SpatialPoints')
heavytraffic <- readOGR(dsn = "final_data",  layer = "heavy_traffic")
heavytraffic_sp <- as(heavytraffic, 'SpatialPoints')
# accidents <- traffic_Report_svy21 %>% filter(Type == "Accident")
# accidents_sp <- as(accidents, "Spatial")
# heavytraffic <- traffic_Report_svy21 %>% filter(Type == "Heavy Traffic")
# heavytraffic_sp <- as(heavytraffic, "Spatial")
accidents_ppp <- ppp(coordinates(accidents_sp)[,1], coordinates(accidents_sp)[,2], costaloutline_owin)
heavytraffic_ppp <- ppp(coordinates(heavytraffic_sp)[,1], coordinates(heavytraffic_sp)[,2], costaloutline_owin)

plot(accidents_ppp)
plot(heavytraffic_ppp)
```

##Preparing the linnet
```{r}
library(maptools)
roadNetwork <- readShapeSpatial("data/RoadNetwork/roads_expressway", CRS("+init=epsg:3414"))
roadNetwork_psp <- as.psp(roadNetwork, window=NULL, marks=NULL, check=spatstat.options("checksegments"), fatal=TRUE)
roadNetwork_linnet <- as.linnet.psp(roadNetwork_psp, sparse=TRUE)
plot(roadNetwork_linnet)
```

##LPP
Generating the LPP

```{r}
accidents_lpp <- lpp(accidents_ppp, roadNetwork_linnet)
heavytraffic_lpp <- lpp(heavytraffic_ppp, roadNetwork_linnet)
plot(accidents_lpp)
plot(heavytraffic_lpp)
```

***
###K Function
Plotting the K function
```{r}
plot(linearK(accidents_lpp, correction="none", ratio=FALSE))
```

***
###Kernel Density Estimation
Plotting the KDE
```{r}
library(spatstat)
plot(density.lpp(accidents_lpp, 1000))
plot(density.ppp(accidents_ppp, sigma=bw.ppl))
plot(density.lpp(heavytraffic_lpp, 3000))
plot(density.ppp(heavytraffic_ppp, 1000))
```


***
###K Nearest Neighbour
Plotting the knn
```{r}
library(spatstat)
hist(nndist.lpp(accidents_lpp, k=10, method="C"))
plot(nnfun.lpp(accidents_lpp, k=10, method="C"))
plot(envelope(accidents_ppp, Gest, nsim = 99, rank = 1, glocal = TRUE), xlim=c(0,10000))
hist(nndist.lpp(heavytraffic_lpp, k=10, method="C"))
plot(nnfun.lpp(heavytraffic_lpp, k=10, method="C"))
plot(envelope(heavytraffic_ppp, Gest, nsim = 99, rank = 1, glocal = TRUE), xlim=c(0,6000))
```

***
###Interactive map on accidents
Storing the accident KDE to variable

```{r}
library(spatstat)
accidentskde <- density.lpp(accidents_lpp, sigma=1000)
accidentskde_ppp <- density.ppp(accidents_ppp, sigma=1000)
plot(accidentskde)
```
Convert accident kde to spatialgriddataframe and using tmap to plot

```{r}
library(tmap)
library(tmaptools)
library(maptools)
library(rgdal)
library(raster)

accidentkde_sgdf <- as.SpatialGridDataFrame.im(accidentskde)

accidentkde_raster <- raster(accidentkde_sgdf)
accidentkde_raster_scaled <- disaggregate(accidentkde_raster, fact=4 ,fun=mean)
#accidentkde_raster_scaled <- scale(accidentkde_raster, center = FALSE, scale = TRUE)

accidentkde_ppp_sgdf <- as.SpatialGridDataFrame.im(accidentskde_ppp)

proj4string(accidentkde_sgdf) = CRS("+init=epsg:3414")
proj4string(accidentkde_raster_scaled) = CRS("+init=epsg:3414")
proj4string(accidentkde_ppp_sgdf) = CRS("+init=epsg:3414")

tmap_mode("view")
tm_shape(accidentkde_raster_scaled) +
  tm_raster() +  #can modify to style the raster
  tm_shape(accidentkde_ppp_sgdf) + 
  tm_raster()
```

***
###Interactive map for heavy traffic
Storing the heavy traffic KDE to variable

```{r}
library(spatstat)
heavytraffickde <- density.lpp(heavytraffic_lpp, sigma=3000)
heavytraffickde_ppp <- density.ppp(heavytraffic_ppp, sigma=500)
```

Convert heavy traffic kde to spatialgriddataframe and using tmap to plot

```{r}
library(tmap)
library(tmaptools)
library(maptools)

heavytraffickde_sgdf <- as.SpatialGridDataFrame.im(heavytraffickde)
heavytraffickde_ppp_sgdf <- as.SpatialGridDataFrame.im(heavytraffickde_ppp)

proj4string(heavytraffickde_sgdf) = CRS("+init=epsg:3414")
proj4string(heavytraffickde_ppp_sgdf) = CRS("+init=epsg:3414")

tmap_mode("view")
qtm(heavytraffickde_ppp_sgdf)
```
