---
title: "R Notebook"
output: html_notebook
---
***
###Creating PPP

Import the traffic dataset and coverting the crs from WGS84 to SVY21, at the same time, fixing the x and y for ppp function later. Result is exported to a temp csv file located in /data.
```{r}
trafficReport <- read_csv("data/LTATrafficDataClean2.csv")
trafficReport_shp <- st_as_sf(trafficReport, coords = c("Longitude", "Latitude"), crs = "+proj=longlat +datum=WGS84 +no_defs")
traffic_Report_svy21 <- st_transform(trafficReport_shp, crs = 3414)
st_write(traffic_Report_svy21, "data/temp.csv", layer_options = "GEOMETRY=AS_XY") # writes X and Y as columns
```

***
Reading the temp csv and creating the ppp
```{r}
temp <- read_csv("data/temp.csv")
accidents <- temp %>% filter(Type == "Accident")
roadworks <- temp %>% filter(Type == "Roadwork")
accidents_ppp <- ppp(accidents$X, accidents$Y, c(min(accidents$X), max(accidents$X)), c(min(accidents$Y), max(accidents$Y)))
roadworks_ppp <- ppp(roadworks$X, roadworks$Y, c(min(roadworks$X), max(roadworks$X)), c(min(roadworks$Y), max(roadworks$Y)))
plot(accidents_ppp)
plot(roadworks_ppp)
```

##Preparing the linnet
```{r}
roadNetwork <- readShapeSpatial("data/RoadNetwork/roads_expressway")
roadNetwork_psp <- as.psp(roadNetwork, window=NULL, marks=NULL, check=spatstat.options("checksegments"), fatal=TRUE)
roadNetwork_linnet <- as.linnet.psp(roadNetwork_psp, sparse=TRUE)
plot(roadNetwork_linnet)
```

##LPP
Generating the LPP

```{r}
accidents_lpp <- lpp(accidents_ppp, roadNetwork_linnet)
```

***
###K Function
Plotting the K function
```{r}
plot(linearK(accidents_lpp, correction="none", ratio=FALSE))
```

***
###Kernel Density Estimation
Plotting the KDE
```{r}
plot(density.lpp(accidents_lpp, 1000))
```

***
###K Nearest Neighbour
Plotting the knn
```{r}
plot(nndist.lpp(accidents_lpp, k=10, method="C"))
```


